---
editor_options:
  chunk_output_type: inline
output:
  html_notebook: 
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
library(devtools)
```

# `tidypmc` - package review

## **Reviewer:** [\@toph-allen](https://github.com/toph-allen)

### Review Submitted:
**`r cat(sprintf("**Last updated:** %s", Sys.Date()))`**

***

<br>

This report contains documents associated with the review of **rOpenSci** submitted package:

### **`tidypmc`: ropensci/software-review**  issue [\#290](https://github.com/ropensci/onboarding/issues/290).

<br>

## Package info

**Description:**

This package parses section paragraphs, captions, tables, references and metadata from XML documents in the Open Access subset of Pubmed Central. Additional functions are available to search text and expand ranges of the references cited, locus tags and gene operons.

**Author:** `r `

**repo url:** <https://github.com/cstubben/tidypmc>

**website url:** <>

## Review info


#### See [reviewer guidelines](https://ropensci.github.io/dev_guide/reviewerguide.html) for further information on the rOpenSci review process.

**key review checks:**

- Does the code comply with **general principles in the [Mozilla reviewing guide](https://mozillascience.github.io/codeReview/review.html)**?
- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
- Are there **improvements** that could be made to the **code style?**
- Is there **code duplication** in the package that should be reduced?
- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?
- Is the [**documentation**](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) **clear and sufficient**?

Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://ropensci.github.io/dev_guide/policies.html#code-of-conduct) is mandatory for everyone involved in our review process.

***

### session info


```{r sessionInfo}
sessionInfo()
```


```{r pkg_dir, echo = F}
pkg_dir <- "/Users/toph/Local/rOpenSci Reviews/tidypmc"
```

## Test installation

### test local `tidypmc` install:

```{r test-local}
install(pkg_dir, dependencies = T, build_vignettes = T)
```

```{r github-rm}
remove.packages("tidypmc")
```
#### **comments:**

<!-- record comments on local install here  -->

***

### test install of `tidypmc` from GitHub with:

```{r test-github}
devtools::install_github("cstubben/tidypmc", dependencies = T, build_vignettes = T)
```

#### **comments:**

All checks out nicely.

***



## Check package integrity

### run checks on `tidypmc` source:

```{r check-checks}
devtools::check(pkg_dir)
```
#### **comments:**

Looks good. There is one "note" returned about extdata being 8 Mb.

***

### run tests on `tidypmc` source:

```{r check-tests}
devtools::test(pkg_dir)
```
#### **comments:**

All ok!

***


### check `tidypmc` for goodpractice:

```{r test-goodpractice}
goodpractice::gp(pkg_dir)
```
#### **comments:**

Got a warning about 22% of code not being covered by tests, and the same `extdata` directory being over 1 Mb.

***

## Check package metadata files

### inspect

- #### [README](https://github.com/cstubben/tidypmc)
- #### [DESCRIPTION](https://github.com/cstubben/tidypmc/blob/master/DESCRIPTION)
- #### [NAMESPACE](https://github.com/cstubben/tidypmc/blob/master/NAMESPACE)

### spell check

```{r spell-check}
devtools::spell_check(pkg_dir)
```

#### **comments:**

This all looks fine.

***

## Check documentation

online documentation: **<>**

* Is the [documentation](https://ropensci.github.io/dev_guide/building.html#documentation) (installation instructions/vignettes/examples/demos) clear and sufficient?

### test `tidypmc` function help files:

```{r test-help}
help(package = "tidypmc")
```

#### **comments:**

The help page isn't loading for me right now. I'm going to try again after a restart.

***

### test `tidypmc` vignettes:

```{r test-vignettes}
vignette(package = "tidypmc")
```

#### **comments:**

None found.

***

## Test functionality:

- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?

```{r free-style}
library("tidypmc")
```

```{r parse-functions}
exports <-ls("package:tidypmc")
exports
```

<!-- experiment with package functions -->

```{r exp-chunk}


```

#### **comments:**

<!-- record comments on package experimentation here -->

***

## Inspect code:

- Does the package **comply with the [ROpenSci packaging guide](https://ropensci.github.io/dev_guide/building.html)**?
    * good [function & variable naming?](https://ropensci.github.io/dev_guide/building.html#function-and-argument-naming)
    * good [dependency management](https://ropensci.github.io/dev_guide/building.html#package-dependencies)?
- Are there **improvements** that could be made to the [**code style?**](https://ropensci.github.io/dev_guide/building.html#code-style)
- Is there **code duplication** in the package that should be reduced?

```{r inspect-code}
pkgreviewr::pkgreview_print_source("tidypmc")
```
**\* might not be suitable for large packages with many exported functions**


<br>
<br>

#### **comments:**

<!-- record comments on package source code here -->


## Review test suite:

See guidance on [testing](https://ropensci.github.io/dev_guide/building.html#testing) for further details.

### test coverage

```{r pkg_coverage}
covr::package_coverage(pkg_dir)

```

### inspect [tests](https://github.com/cstubben/tidypmc/blob/master/tests/testthat)


#### **comments:**

<!-- record comments on testing suite here -->


***
